Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-05 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] changed footnote 1

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematical region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{The
  {logarithmically enhanced NLO QED corrections} to $B\to
  X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's
  comment?!}

This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).

>>>>

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and
scalar couplings has been presented in \cite{Bobeth:2007dw,
  Bobeth:2012vn}, adopting the effective theory \refeq{eq:Heff},
i.e. neglecting higher-dimensional operators with {$\mbox{dim} \geq
  8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2}
    {\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests.
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed {by
  small lepton masses for the considered kinematical region $1 \leq
  q^2 \leq 22$ GeV$^2$} \cite{Bobeth:2007dw, Bobeth:2011nj,
  Bouchard:2013eph}.  Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$
can be induced by higher-order QED corrections, which will modify the
simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no
solid estimate available for this source of SM background\footnote{
  Logarithmically enhanced NLO QED corrections to $B\to X_s
  \bar\ell\ell$~\cite{Huber:2015sra} turn out to be non-negligible
  for angular observables,
  however, analogous corrections to $B\to K \bar\ell\ell$ are partially 
  included in the event simulation of the experimental 
  analysis~\cite{Aaij:2014tfa} via PHOTOS~\cite{Golonka:2005pn}. 
  As proposed in \cite{Gratrex:2015hna}, the measurement of higher
  moments of the decay distribution~\refeq{eq:ang-distr} could give an 
  estimate of the size of higher-order QED corrections, but still
  admixed with contributions of $\mbox{dim} \geq 8$ operators.}. 
This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
nonvanishing tensor or scalar contributions are enhanced unless the dynamics of
NP implies similar suppression factors, i.e., lepton-Yukawa couplings for
$F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings (see \refeq{eq:AFB-dependence}
below) and $A_{\rm FB}^\ell$ is sensitive to the interference of tensor and
scalar couplings (see \refeq{eq:FH-dependence} below).
